\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-12 adaptive-estimation.tex
Working on the regularity stupidity

Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
on the asymptotic normality of averaged stochastic gradient estimators
to establish the following theorem.
\begin{thm}
  \label{thm:sgd}
  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
  \sum_{i = 1}^n \theta_i$. Assume
  that in a neighborhood
  of $\theta = \mbox{med}(P)$,
  the distribution $P$ has a Lipschitz continuous density $f$.
  Then
  \begin{enumerate}[(i)]
  \item \label{item:normal-sgd}
    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
    Then
    \begin{equation*}
      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
      \cd \normal\left(0,\frac{1}{4 f(\theta)^2}\right).
    \end{equation*}
    %
    %
  \item
    Assume in addition that $f(x)$ is continuously differentiable with a
    finite Fisher information
    \begin{equation*}
      \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
    \end{equation*}
    for the location in the family $\{P_\theta\}$.
    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
    Then for any bounded, symmetric, and quasi-convex function $L$, 
    \begin{align} 
      & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
      \\
      & \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
    \end{align}
    where $Z \sim \Ncal(0,1)$. 
    %
    %
  \item Assume the stepsizes $\gamma_n$ satisfy both
    conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.
    Then
    \begin{equation*}
      \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{4 n f(\theta)^2} + o(n^{-1}). 
    \end{equation*}
  \end{enumerate}
\end{thm}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm,auto]
  \node at (0,0) (source) {$X_1$} ;
  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
\draw[->,line width = 2pt] (source) -- (enc1);

% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
%\draw[->,line width = 2pt] (source2) -- (enc2);

\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};

\draw[->,line width = 2pt] (source3) -- (enc3);

\node[below of = source, node distance = 0.5cm] {$\vdots$};

\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};

\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);

%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);

\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);

\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
\draw[->,line width = 2pt] (sourceB) -- (enc1B);

\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
\draw[->,line width = 2pt] (source3B) -- (enc3B); 
\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};

\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};

\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);

\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);

%\draw[->,line width = 1pt] (enc1B) -- (enc3B);

\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);

%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);

\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};

\end{tikzpicture}
\end{center}
\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
\label{fig:one_round}
}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.6]
\begin{axis}[
width=10cm, height=6cm,
xmin = 0, xmax=800, 
restrict y to domain = 0:3,
ymin = 0,
ymax = 3.4,
samples=10, 
xlabel= $n$,
ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
%xtick={-3,-2,-1,0,1,2,3},
%xticklabels={-3,-2,-1,0,1,2,3},
ytick={0,1,1.57},
yticklabels={0,1,$\pi/2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]

\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
\addlegendentry{asymptotically optimal};

%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};

\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
\addlegendentry{single interaction};

\end{axis}
\end{tikzpicture}
%\begin{tikzpicture}
%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
%\node[scale = 0.7] at (0,-2.4) {$n$};
%\end{tikzpicture}
\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density. In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$. The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage. 
\label{fig:adaptive_error}  }
\end{center}
\end{figure}

>>>>

Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
on the asymptotic normality of averaged stochastic gradient estimators
to establish the following theorem.
\begin{thm}
  \label{thm:sgd}
  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
  \sum_{i = 1}^n \theta_i$. Assume
  that in a neighborhood
  of $\theta = \mbox{med}(P)$,
  the distribution $P$ has a Lipschitz continuous density $f$.
  Then
  \begin{enumerate}[(i)]
  \item \label{item:normal-sgd}
    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
    Then
    \begin{equation*}
      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
      \cd \normal\left(0,\frac{1}{4 f(\theta)^2}\right).
    \end{equation*}
    %
    %
  \item \label{item:sgd-regular}
    Assume in addition that $f(x)$ is continuously differentiable with a
    finite Fisher information
    \begin{equation*}
      \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
    \end{equation*}
    for the location in the family $\{P_\theta\}$.
    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
    Then for any bounded, symmetric, and quasi-convex function $L$, 
    \begin{align} 
      & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
      \\
      & \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
    \end{align}
    where $Z \sim \Ncal(0,1)$. 
    %
    %
  \item Assume the stepsizes $\gamma_n$ satisfy both
    conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.
    Then
    \begin{equation*}
      \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{4 n f(\theta)^2} + o(n^{-1}). 
    \end{equation*}
  \end{enumerate}
\end{thm}

@@

%% \begin{figure}
%% \begin{center}
%% \begin{tikzpicture}[node distance=2cm,auto]
%%   \node at (0,0) (source) {$X_1$} ;
%%   \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
%% \draw[->,line width = 2pt] (source) -- (enc1);

%% % \node[below of = source, node distance = 1cm] (source2) {$X_2$};
%% %\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
%% %\draw[->,line width = 2pt] (source2) -- (enc2);

%% \node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
%% \node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};

%% \draw[->,line width = 2pt] (source3) -- (enc3);

%% \node[below of = source, node distance = 0.5cm] {$\vdots$};

%% \node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};

%% \draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);

%% %\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);

%% \draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);

%% \node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
%% \node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
%% \draw[->,line width = 2pt] (sourceB) -- (enc1B);

%% \node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
%% \node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
%% \draw[->,line width = 2pt] (source3B) -- (enc3B); 
%% \node[below of = sourceB, node distance = 0.4cm] {$\vdots$};

%% \node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};

%% \draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
%% \draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);

%% \draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);

%% %\draw[->,line width = 1pt] (enc1B) -- (enc3B);

%% \draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);

%% %\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);

%% \draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
%% \node[below of = enc1B, node distance = 0.5cm] {$\vdots$};

%% \end{tikzpicture}
%% \end{center}
%% \caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
%% \label{fig:one_round}
%% }
%% \end{figure}

@@

%% \begin{figure}
%% \begin{center}
%% \begin{tikzpicture}[scale = 0.6]
%% \begin{axis}[
%% width=10cm, height=6cm,
%% xmin = 0, xmax=800, 
%% restrict y to domain = 0:3,
%% ymin = 0,
%% ymax = 3.4,
%% samples=10, 
%% xlabel= $n$,
%% ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
%% %xtick={-3,-2,-1,0,1,2,3},
%% %xticklabels={-3,-2,-1,0,1,2,3},
%% ytick={0,1,1.57},
%% yticklabels={0,1,$\pi/2$},
%% line width=1.0pt,
%% mark size=1.5pt,
%% ymajorgrids,
%% xmajorgrids,
%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
%% ]

%% \addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
%% \addlegendentry{asymptotically optimal};

%% %\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};

%% \addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
%% \addlegendentry{single interaction};

%% \end{axis}
%% \end{tikzpicture}
%% %\begin{tikzpicture}
%% %\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
%% %\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
%% %\node[scale = 0.7] at (0,-2.4) {$n$};
%% %\end{tikzpicture}
%% \caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density. In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$. The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage. 
%% \label{fig:adaptive_error}  }
%% \end{center}
%% \end{figure}
